\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-01-27 background.tex
Updated the paper

The perfect synchrony hypothesis is ideal for programming the
synchronous sub-set of SystemJ. Unfortunately, every \textit{micro-step}
requires real-time to compute. Formally, execution of every micro-step
in the logical zero time requires $\delta$ physical time. Time for a
logical tick can thus be summarized as $\Delta = \mathcal{F} (\delta)$,
where $\mathcal{F}$ is some function dependent upon the
\underline{schedule}. We call $\Delta$ the reaction time. Depending upon
the amount of computation required and schedule, $\Delta$ can vary,
hence, in order to satisfy the implicit restriction imposed by the
synchrony hypothesis -- no input event \textit{from the environment} can
be missed -- one needs to calculate the \textit{Worst Case Reaction
  Time} (WCRT) and the resultant WCRT needs to be smaller than the time
between any two consecutive events on any input, else the synchrony
hypothesis is violated. Techniques for calculating the WCRT of
synchronous programs~\cite{boldt07} exist and this analysis is not the
focus of this paper. The opposite of the WCRT is the \textit{Best Case
  Reaction Time} (BCRT), we denote the WCRT and BCRT in
Figure~\ref{fig:2c} using \texttt{W} and \texttt{B},
respectively. Figure~\ref{fig:2c} shows a continuously running physical
clock (analogous to a clock in digital hardware), the numerical
annotations on the rising edge of the clock mark the logical ticks from
Figure~\ref{fig:2c}. The subscripts \texttt{s} and \texttt{e} for the
numbers show the start and end of the logical ticks, respectively. The
end of a logical tick and the start of the next logical tick happen
together. Figure~\ref{fig:2c} shows the mapping of the logical time to
the physical time. For example, the logical tick \texttt{1} starts at
the first rising edge and completes at the second rising edge of the
physical clock, whereas logical tick \texttt{4} starts at the $4^{th}$
rising edge, but finishes at the $6^{th}$ rising edge of the physical
clock. This difference can be accounted for by the Java computations
required when signal \texttt{A} is input by the environment (see
Figure~\ref{fig:2a}). This elasticity is inherent (and elegant) to both
Esterel and SystemJ.

>>>>

The perfect synchrony hypothesis is ideal for programming the
synchronous sub-set of SystemJ. Unfortunately, every \textit{micro-step}
requires real-time to compute. Formally, execution of every micro-step
in the logical zero time requires $\delta$ physical time. Time for a
logical tick can thus be summarized as $\Delta = \mathcal{F} (\delta)$,
where $\mathcal{F}$ is some function dependent upon the
\underline{schedule}. We call $\Delta$ the reaction time. Depending upon
the amount of computation required and schedule, $\Delta$ can vary,
hence, in order to satisfy the implicit restriction imposed by the
synchrony hypothesis -- no input event \textit{from the environment} can
be missed -- one needs to calculate the \textit{Worst Case Reaction
  Time} (WCRT) and the resultant WCRT needs to be smaller than the time
between any two consecutive events on any input, else the synchrony
hypothesis is violated. Techniques for calculating the WCRT of
synchronous programs~\cite{boldt07} exist and this analysis is not the
focus of this paper. The opposite of the WCRT, the shortest time for a
reaction, is called the \textit{Best Case Reaction Time} (BCRT), we
denote the WCRT and BCRT in Figure~\ref{fig:2c} using \texttt{W} and
\texttt{B}, respectively. Figure~\ref{fig:2c} shows a continuously
running physical clock (analogous to a clock in digital hardware), the
numerical annotations on the rising edge of the clock mark the logical
ticks from Figure~\ref{fig:2c}. The subscripts \texttt{s} and \texttt{e}
for the numbers show the start and end of the logical ticks,
respectively. The end of a logical tick and the start of the next
logical tick happen together. Figure~\ref{fig:2c} shows the mapping of
the logical time to the physical time. For example, the logical tick
\texttt{1} starts at the first rising edge and completes at the second
rising edge of the physical clock, whereas logical tick \texttt{4}
starts at the $4^{th}$ rising edge, but finishes at the $6^{th}$ rising
edge of the physical clock. This difference can be accounted for by the
Java computations required when signal \texttt{A} is input by the
environment (see Figure~\ref{fig:2a}). This elasticity is inherent (and
elegant) to both Esterel and SystemJ.

### 2014-01-27 conclusion.tex
Updated the paper

\section{Background}
\label{sec:background}

>>>>

\section{Conclusion}
\label{sec:concl-future-work}

In this paper we have described a novel way to introduce real-time in
\textit{Globally Asynchronous Locally Synchronous} (GALS) languages, in
particular SystemJ, and their subset the synchronous languages like
Esterel. The fundamental idea is to convert real-time wait constructs
into logical waits (\texttt{pause} construct) that interact well with
rest of the constructs in these languages, especially, preemption and
channel communication. We do \textit{not} need or use external timers to
introduce these real-time wait constructs, instead we depend upon an
underlying platform that is timing analyzable, thereby resolving the
problems of interaction between external timers and
preemption. Moreover, we also do not require specific timer resolutions,
thereby making our solution elegant (in the spirit of GALS/synchronous
programming) and flexible. We rewrite the wait constructs into reactive
kernel constructs, calculate the \textit{Worst} and \textit{Best} case
reaction times and then determine wait \texttt{d} in number of logical
ticks, which is invariant to the \textit{elasticity} of logical time. To
our knowledge we are the first to introduce exact and inexact wait
constructs in such languages and show their usefulness in designing
real-world systems.

### 2014-01-27 delays.tex
Updated the paper

We introduce a single \textit{derived} (built from kernel constructs)
statement called \mbox{\texttt{delay (M..N)}} in the SystemJ language
for real-time control. The resolution of the delay statement is of
secondary concern and is dependent upon the execution platform.

\subsection{Semantics of the delay statement}
\label{sec:semant-delay-stat}

\begin{figure}[t!]
  \centering
  \includegraphics[scale=0.6]{./sem}
  \caption{Pictorial representation of the semantics of the delay
    statement and its variants}
  \label{fig:5}
\end{figure}

Given a SystemJ program: \texttt{delay (M..N); p}, where $M \in
\mathbb{Q}^{>0}$ and $N \in \mathbb{Q}^{>0}$, statement $p$ is executed
after real-time delay of $\tau$ units, such that, $M \leq \tau \leq N$.

We also introduce two variants of the derived statement \texttt{delay}.
\begin{enumerate*}
\item Given a SystemJ program \texttt{delay (M); p}, where $M \in
  \mathbb{Q}^{>0}$, statement $p$ is executed after real-time delay of
  $\tau$ units, such that, $M \leq \tau < \infty$. It is important to
  note that the lower bound of the delay construct $M$ is \textit{not}
  an exact delay, but rather the control is allowed to proceed to the
  next statement anytime after the delay of time $M$.
\item Given a SystemJ program \texttt{delay (M..M); p}, where $M \in
  \mathbb{Q}^{>0}$, statement $p$ is executed after real-time delay of
  $\tau$ units, such that, $M \leq \tau \leq M$. In this variant, the
  delay is exact.
\end{enumerate*}

Figure~\ref{fig:5} pictorially represents the semantics of these delay
constructs. The construct \texttt{delay (M..N)} requires that upon
execution the control-flow is suspended for \textit{at least} $M$ units
and \textit{at most} $N$ units, depicted as bounded box in
Figure~\ref{fig:5}. There is no upper bound for the second delay variant
\texttt{delay(M)}, which requires that the control-flow suspends for
\textit{at least} $M$ units, but the following statement can be executed
after some countable delay, depicted with the unbounded box in
Figure~\ref{fig:5}. Finally, \texttt{delay (M..M)} requires that there
is an \textit{exact} delay of $M$ units, i.e., the control-flow suspends
execution for \textit{at least} and \textit{at most} $M$ units.

\subsection{Rewriting the \texttt{delay} statement}
\label{sec:rewr-delay-stat}

The introduced \texttt{delay} construct is not a kernel construct, but a
\textit{derived} construct built from the kernel constructs
(Table~\ref{tab:1}) in SystemJ. Figure~\ref{fig:3} gives the rewrite of
the \texttt{delay} construct to kernel statements.

\begin{figure}[tb]
	\vspace{-10pt}
    \begin{minipage}{\textwidth}
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
trap(T){
 int x = 0;
 while(true){
  x = x + 1;
  pause;
  if(x == d) exit (T); //wait for "d" ticks
 } // d is the number of logical ticks calculated
} // by Algorithm 1
\end{lstlisting}
    \end{minipage}
    \caption{The rewrite of \texttt{delay} construct}
    \label{fig:3}
\end{figure}

The fundamental observation is that real-time is converted into logical
time via the \texttt{pause} construct. The rewrite basically maps the
physical notion of time back to the elegant logical notion of time. The
rewrite \textit{delays} a certain number of logical ticks, before
proceeding to the next statement. The number of logical ticks \texttt{d}
to \textit{delay} (Figure~\ref{fig:3}) is determined by the compiler
statically at compile time. The value of \texttt{d} is intricately tied
with the WCRT and BCRT of the program and hence the execution platform.

\subsection{Finding the logical delay \texttt{d}}
\label{sec:find-logic-delay}

@@

The computation of \texttt{d} is shown in Algorithm~\ref{alg:1}. This
algorithm is carried out for each CD (in SystemJ) or a synchronous
program individually. \textit{The fundamental observation is -- the
  reaction time for each logical tick is elastic -- varying only between
  the BCRT and the WCRT, thus any number of logical ticks \texttt{d}
  that map to the required real-time \texttt{delay} should be chosen in
  such a way that they are invariant to this elasticity.}

Our algorithm takes as input: WCRT, BCRT, and the lower and upper bounds
$M$ and $N$, respectively of the \texttt{delay} construct. We first
divide $M$ and $N$ with the BCRT and WCRT, respectively. This division
gives us the number of individual logical ticks required to delay the CD
(or synchronous program) by the real-time specification. We always
$ceil$ when dividing $M$ and $floor$ when dividing $N$ to make sure that
the resultant values are integers (in domain $\mathbb{N}^{>0}$) and
these functions guarantee that the resultant logical ticks result in
real-time delays between the required range $[M,N]$. Next, a function
$F$ maps these calculated values to a set of equidistant integer points
(values) separated by a unit value -- these points represent all the
logical ticks running at the WCRT and the BCRT, respectively that
satisfy the real-time delay requirements. The intersection of these two
sets gives all the logical ticks that satisfy the real-time requirements
invariant of the logical time and its elasticity.

@@

\begin{enumerate*}
\item $l_1 \leftarrow \lceil 50.3/0.112 \rceil$ and $u_1 \leftarrow
  \lfloor 200.3/0.112 \rfloor$. $l_1 = 450$ and $u_1 = 1788$. We first
  calculate the logical ticks that are always running at the WCRT and
  satisfy the required real-time delay.
\item $l_2 \leftarrow \lceil 50.3/0.0334 \rceil$ and $u_2 \leftarrow
  \lfloor 200.3/0.0334 \rfloor$. $l_1 = 1506$ and $u_1 = 5997$. We do
  the same for the BCRT case.
\item $S_1 = [450,1788]$ and $S_2 =[1506,5997]$. We then map the
  resultant bounds to linear points. Sets $S_1$ and $S_2$ represent
  logical ticks that running at the WCRT and BCRT, respectively always
  satisfy the required real-time constraints.
\item $D = S_1 \cap S_2$, $D = [1506,1788]$. Finally, the intersection
  of the two sets gives the set $D$ from which we can choose any value
  for \texttt{d}.
\end{enumerate*}

The resultant value for \texttt{d} gives the number of logical ticks,
which can run at any physical clock-speed, bounded by the BCRT and the
WCRT of the program and still result in the desired real-time delay. We
think this is an elegant solution, because the technique provides
real-time guarantees while preserving the essence (elastic logical tick)
of synchronous and GALS programming prescribed by SystemJ and Esterel
style languages. Moreover, this technique considers non
maximal-parallelism, i.e., the delay in logical ticks is calculated
after scheduling of CDs or synchronous programs has been performed. To
our knowledge we are the first to do so.

\subsection{Extending the technique to variants of \texttt{delay}}
\label{sec:extend-tehcn-vari}

\paragraph{The \texttt{delay(M)} construct}
\label{sec:extend-techn-vari}

The \texttt{delay(M)} variant is easily accommodated in the
technique. All one needs to do is find the set $S_1$ and choose a value
from this set.

\paragraph{The \texttt{delay(M..M)} construct}
\label{sec:extend-techn-vari}

The \texttt{delay(M..M)} variant is more interesting. Like before, we
find sets $S_1$ and $S_2$, and find the intersection of the two sets to
get the value of \texttt{d}. It is possible (and often likely, as
suggested by our experiments in Section~\ref{sec:experimental-results})
that the resultant set $D$ is empty (also possible in the case of
\texttt{delay(M..N)}, but never possible in case of
\texttt{delay(M)}). Note that $S_1$ and $S_2$ can never be empty sets
and will always contain at minimum a single element. In such a case, we
can \textit{relax} the upper bound of the \texttt{delay} statement.

@@

This algorithm results in the \underline{smallest} relaxation required
for the real-time delay to be satisfied. The algorithm takes as input
the WCRT and set $S_2$, recall that set $S_2$ represents the logical
ticks required to satisfy the real-time requirement at the BCRT. We take
the very first value from set $S_2$ and multiply it with the WCRT to get
the relaxation $N$. The first element of set $S_2$ is returned as the
logical tick delay \texttt{d}. The fundamental observation is that we
have to delay for at least $M$ units of real-time, hence,
under-approximation is out of question. We can still over-approximate,
but to reduce the resultant error, we should over-approximate by least
possible value, which is the lower bound of set $S_2$. Thus, the lower
bound is considered to be the only element shared between the two sets
$S_1$ and $S_2$ and accordingly, the upper real-time bound is relaxed by
the multiplication of WCRT and the first element of set $S_2$.

For example, assume $BCRT=5$ and $WCRT=100$, with a required delay of
$(200..200)$. Algorithm~\ref{alg:1}, results in $D$ being an empty set,
since $S_1=[2]$ and $S_2=[40]$, respectively. In such a case, the
resultant relaxation is: $40 \times 100$ using Algorithm~\ref{alg:2},
which results in a time of $4000$ units. Such large over-approximations
can be avoided by breaking the critical paths (worst case ticks) in the
program (by inserting \texttt{pause} constructs), just like in hardware
design, which is very \textit{unsurprising} considering Esterel has its
origins in hardware.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.45]{./tool.pdf}
  \caption{The tool-chain flow of SystemJ compiler with delays}
  \label{fig:4}
\end{figure}

The interaction of the low-level execution platform and the described
high-level technique of introducing real-time delays in the SystemJ
language is shown in Figure~\ref{fig:4}. We use static-analysis
techniques to find out the WCRT/BCRT of the programs automatically after
rewrites and standard compiler optimizations. We require timing
analyzable platforms, in our case \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}. Moreover, since algorithms~\ref{alg:1}
and~\ref{alg:2} are performed after scheduling for different constraints
such as faster execution time, or reduced power consumption, we,
inherently satisfy the criteria of exploiting non-maximal
parallelism. The low-level analysis guarantees a precise WCRT/BCRT for
the logical tick, which is then used for calculating $d$ in
Figure~\ref{fig:3}.

Our compiler has a switch that enables over-approximation as described
in Section~\ref{sec:extend-tehcn-vari} provided the delay requirements
are not met. If this compiler switch is not enabled, the compiler simply
outputs an error indicating the relaxation required. The system designer
can then either set the compiler switch or change the program by
shortening the critical path by introducing \texttt{pause}
constructs. We show how introducing \texttt{pause} constructs can help
reduce the WCRT in Section~\ref{sec:experimental-results}.

>>>>

We introduce a single \textit{derived} statement called
\mbox{\texttt{wait\_inbetween (M..N)}}, built from kernel constructs, in
the SystemJ language for real-time control. The other two constructs
\mbox{\texttt{wait\_atleast (M)}} and \mbox{\texttt{wait\_exactly (M)}}
are variants of this single derived construct.

% The resolution of the delay statement is of secondary concern and is
% dependent upon the execution platform.

\subsection{Semantics of the \texttt{wait\_inbetween} statement}
\label{sec:semant-delay-stat}

% \begin{figure}[t!]
%   \centering
%   \includegraphics[scale=0.6]{./sem}
%   \caption{Pictorial representation of the semantics of the delay
%     statement and its variants}
%   \label{fig:5}
% \end{figure}

Given a SystemJ program: \texttt{wait\_inbetween (M..N); p}, where $M
\in \mathbb{Q}^{>0}$ and $N \in \mathbb{Q}^{>0}$, statement $p$ is
executed after real-time delay of $\tau$ units, such that, $M \leq \tau
\leq N$.

We also introduce two variants of the derived statement
\texttt{wait\_inbetween}.
\begin{enumerate*}
\item Given a SystemJ program \texttt{wait\_atleast (M); p}, where $M
  \in \mathbb{Q}^{>0}$, statement $p$ is executed after real-time delay
  of $\tau$ units, such that, $M \leq \tau < \infty$. It is important to
  note that the lower bound of the wait construct; $M$ is \textit{not}
  an exact delay, but rather the control is allowed to proceed to the
  next statement anytime after waiting for \textit{at least} time $M$.
\item Given a SystemJ program \texttt{wait\_exactly (M); p}, where $M
  \in \mathbb{Q}^{>0}$, statement $p$ is executed after real-time delay
  of $\tau$ units, such that, $M \leq \tau \leq M$. In this variant, the
  waiting time is exact.
\end{enumerate*}

% Figure~\ref{fig:5} pictorially represents the semantics of these delay
% constructs. The construct \texttt{delay (M..N)} requires that upon
% execution, the control-flow is suspended for \textit{at least} $M$ units
% and \textit{at most} $N$ units, depicted as bounded box in
% Figure~\ref{fig:5}. There is no upper bound for the delay variant
% \texttt{delay(M)}, which requires that the control-flow suspends for
% \textit{at least} $M$ units, but the following statement can be executed
% after some countable delay, depicted with the unbounded box in
% Figure~\ref{fig:5}. Finally, \texttt{delay (M..M)} requires that there
% is an \textit{exact} delay of $M$ units, i.e., the control-flow suspends
% execution for \textit{at least} and \textit{at most} $M$ units.

\subsection{Rewriting the \texttt{wait\_inbetween} statement}
\label{sec:rewr-delay-stat}

The introduced \texttt{wait\_inbetween} construct is not a kernel
construct, but a \textit{derived} construct built from the kernel
constructs (Table~\ref{tab:1}) in SystemJ. Figure~\ref{fig:3} gives the
rewrite of the \texttt{wait\_inbetween} construct to kernel statements.

\begin{figure}[tb]
	\vspace{-10pt}
    \begin{minipage}{\textwidth}
      \begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
trap(T){
 int x = 0;
 while(true){
  x = x + 1;
  pause;
  if(x == d) exit (T); //wait for "d" ticks
 } // d is the number of logical ticks calculated
} // by Algorithm 1
\end{lstlisting}
    \end{minipage}
    \caption{The rewrite of \texttt{wait\_inbetween} construct}
    \label{fig:3}
\end{figure}

The fundamental observation is that real-time is converted into logical
time via the \texttt{pause} construct. The rewrite basically maps the
physical notion of time back to the elegant logical notion of time. The
rewrite \textit{waits} a certain number of logical ticks, before
proceeding to the next statement. The number of logical ticks \texttt{d}
to \textit{wait} (Figure~\ref{fig:3}) is determined by the compiler
statically at compile time. The value of \texttt{d} is intricately tied
with the WCRT and BCRT of the program and hence the execution platform.

\subsection{Finding the logical wait \texttt{d}}
\label{sec:find-logic-delay}

@@

The computation of \texttt{d} is shown in Algorithm~\ref{alg:1}. This
algorithm is carried out for each CD (in SystemJ) or a synchronous
program individually. \textit{The fundamental observation is -- the
  reaction time for each logical tick is elastic -- varying only between
  the BCRT and the WCRT, thus any number of logical ticks \texttt{d}
  that map to the required real-time \mbox{\texttt{wait\_inbetween
      (M..N)}} should be chosen in such a way that they are invariant to
  this elasticity.}

Our algorithm takes as input: WCRT, BCRT, and the lower and upper bounds
$M$ and $N$, respectively of the \texttt{wait\_inbetween} construct. We
first divide $M$ and $N$ with the BCRT and WCRT, respectively. This
division gives us the number of individual logical ticks required to
postpone the CD (or synchronous program) by the real-time
specification. We always $ceil$ when dividing $M$ and $floor$ when
dividing $N$ to make sure that the resultant values are integers (in
domain $\mathbb{N}^{>0}$) and these functions guarantee that the
resultant logical ticks result in real-time postponements between the
required range $[M,N]$. Next, a function $F$ maps these calculated
values to a set of equidistant integer points (values) separated by a
unit value -- these points represent all the logical ticks running at
the WCRT and the BCRT, respectively that satisfy the real-time wait
requirements. The intersection of these two sets gives all the logical
ticks that satisfy the real-time requirements invariant of the logical
time and its elasticity.

@@

\begin{enumerate*}
\item $l_1 \leftarrow \lceil 50.3/0.112 \rceil$ and $u_1 \leftarrow
  \lfloor 200.3/0.112 \rfloor$. $l_1 = 450$ and $u_1 = 1788$. We first
  calculate the logical ticks that are always running at the WCRT and
  satisfy the required real-time wait.
\item $l_2 \leftarrow \lceil 50.3/0.0334 \rceil$ and $u_2 \leftarrow
  \lfloor 200.3/0.0334 \rfloor$. $l_1 = 1506$ and $u_1 = 5997$. We do
  the same for the BCRT case.
\item $S_1 = [450,1788]$ and $S_2 =[1506,5997]$. We then map the
  resultant bounds to linear points. Sets $S_1$ and $S_2$ represent
  logical ticks that running at the WCRT and BCRT, respectively always
  satisfy the required real-time constraints.
\item $D = S_1 \cap S_2$, $D = [1506,1788]$. Finally, the intersection
  of the two sets gives the set $D$ from which we can choose any value
  for \texttt{d}.
\end{enumerate*}

\begin{figure}[t!]
  \centering
  \includegraphics[scale=0.6]{FF4}
  \caption{The pictorial representation of the solution for the HRTCS system}
  \label{fig:hrtcssoln}
\end{figure}

The resultant value for \texttt{d} gives the number of logical ticks,
which can run at any physical clock-speed, bounded by the BCRT and the
WCRT of the program and still result in the desired real-time
wait. Figure~\ref{fig:hrtcssoln} gives the solution space for the
aforementioned calculation. The patterned space is the only overlapping
region and hence gives the solution space for the above example.

We think this is an elegant solution, because the technique provides
real-time guarantees while preserving the essence (elastic logical tick)
of synchronous and GALS programming prescribed by SystemJ and Esterel
style languages. Moreover, this technique considers non
maximal-parallelism, i.e., the postponement in logical ticks is
calculated after scheduling of CDs or synchronous programs has been
performed. To our knowledge we are the first to do so.

\subsection{Extending the technique to variants of wait}
\label{sec:extend-tehcn-vari}

\paragraph{The \texttt{wait\_atleast(M)} construct}
\label{sec:extend-techn-vari}

The \texttt{wait\_atleast(M)} variant is easily accommodated in the
technique. All one needs to do is find the set $S_1$ and choose a value
from this set.

\paragraph{The \texttt{wait\_exactly(M)} construct}
\label{sec:extend-techn-vari}

The \texttt{wait\_exactly(M)} variant is more interesting. Like before,
we find sets $S_1$ and $S_2$, and find the intersection of the two sets
to get the value of \texttt{d}. It is possible % (and often likely, as
% suggested by our experiments in
% Section~\ref{sec:experimental-results})
that the resultant set $D$ is empty (also possible in the case of
\texttt{wait\_inbetween(M..N)}, but never possible in case of
\texttt{wait\_atleast(M)}). Note that $S_1$ and $S_2$ can never be empty
sets and will always contain at minimum a single element. For such cases
we provide two solutions listed below.

% In such a case, we can \textit{relax} the upper bound of the
% \texttt{delay} statement.

@@

This algorithm results in the \underline{smallest} relaxation required
for the real-time postponement to be satisfied. The algorithm takes as
input the WCRT and set $S_2$, recall that set $S_2$ represents the
logical ticks required to satisfy the real-time requirement at the
BCRT. We take the very first value from set $S_2$ and multiply it with
the WCRT to get the relaxation $N$. The first element of set $S_2$ is
returned as the logical tick \texttt{d}. The fundamental observation is
that we have to postpone the proceeding statement for at least $M$ units
of real-time, hence, under-approximation is out of question. We can
still over-approximate, but to reduce the resultant error, we should
over-approximate by the least possible value, which is the lower bound
of set $S_2$. Thus, the lower bound is considered to be the only element
shared between the two sets $S_1$ and $S_2$ and accordingly, the upper
real-time bound is relaxed by the multiplication of WCRT and the first
element of set $S_2$.

For example, assume $BCRT=5$ and $WCRT=100$, with a required
postponement of $(200..200)$. Algorithm~\ref{alg:1}, results in $D$
being an empty set, since $S_1=[2]$ and $S_2=[40]$, respectively. In
such a case, the resultant relaxation is: $40 \times 100$ using
Algorithm~\ref{alg:2}, which results in a time of $4000$ units. Such
large over-approximations can be avoided by breaking the critical paths
(worst case ticks) in the program (by inserting \texttt{pause}
constructs), just like in hardware design, which is very
\textit{unsurprising} considering Esterel has its origins in hardware.

\paragraph{Period execution of the clock domains}
\label{sec:peri-exec-clock}

The aforementioned technique maintains the essence of synchronous and
GALS programs -- the logical tick, but in doing so is unable to provide
the exact real-time wait of $M$ time units in case of
\texttt{wait\_exactly(M)} statement, thereby violating its
semantics. The second option is to execute the CD periodically at the
WCRT. WCRT determines the execution speed of any CD guaranteeing that no
input events from the environment will be missed
(cf. Section~\ref{sec:mapping-logical-time}). Thus, if we simply execute
the CD at periodically at the WCRT, we can choose the value of
\textit{d} from set $S1$. This technique allows meeting the synchronous
hypothesis, while at the same time guaranteeing the semantics of the
\texttt{wait\_exactly(M)} statement. But, compared to the previous
option, this technique is very inflexible and results in reduced
response time and increased power consumption.

We believe that the designer should be allowed to choose either of these
techniques and hence, provide this option via compiler switches.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.45]{./tool.pdf}
  \caption{The tool-chain flow of SystemJ compiler with waits}
  \label{fig:4}
\end{figure}

The interaction of the low-level execution platform and the described
high-level technique of introducing real-time waits in the SystemJ
language is shown in Figure~\ref{fig:4}. We use static-analysis
techniques to find out the WCRT/BCRT of the programs automatically after
rewrites and standard compiler optimizations. We require timing
analyzable platforms, in our case \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}. Moreover, since algorithms~\ref{alg:1}
and~\ref{alg:2} are performed after scheduling for different constraints
such as faster execution time, or reduced power consumption, we,
inherently satisfy the criteria of exploiting non-maximal
parallelism. The low-level analysis guarantees a precise WCRT/BCRT for
the logical tick, which is then used for calculating $d$ in
Figure~\ref{fig:3}.

Our compiler has a switch that enables over-approximation as described
in Section~\ref{sec:extend-tehcn-vari} provided the wait requirements
are not met. If this compiler switch is not enabled, the compiler simply
decides to execute the CD at the periodically, where the period is the
WCRT. The system designer can then either set the compiler switch or
change the program by shortening the critical path by introducing
\texttt{pause} constructs. We show how introducing \texttt{pause}
constructs can help reduce the WCRT in
Section~\ref{sec:experimental-results}.
